Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-11 cvpr2018.tex

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ 
		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  
			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline

			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The inception-score evaluation on three datasets. The higher score reflects more meaningful synthetic images and higher diversity. The proposed HDGAN outperforms others significantly.} \label{table:score}
\end{table}

>>>>

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.4999\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03^{\star}$		\\ 
		%%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  
			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline
			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
		\end{tabularx} 
	\end{center}
	\vspace{-.4cm}
	\begin{tablenotes}
		\small
		\item $^\star$Recently, it updated to ${10.62{\pm}.19}$ in its latest github.
	\end{tablenotes} \vspace{-.1cm}
	\caption{The inception-score evaluation on three datasets. The higher score reflects more meaningful synthetic images and higher diversity. The proposed HDGAN outperforms others significantly.} \label{table:score}
\end{table}
